
% -------------------------------------------------------
%  English Abstract
% -------------------------------------------------------


\pagestyle{empty}
\begin{latin}
  \textbf{Abstract}
In some of object recognition problems, labeled data may not be available for all categories.
 Zero-shot learning utilizes auxiliary information (also called signatures)
 describing each category in order to find a classifier that can recognize samples
from categories with no labeled instance. %RR It is usually only unseen classes
On the other hand, with recent advances made by deep neural networks in computer vision, a rich representation can be obtained from images
that discriminates different categorizes and therefore a obtaining unsupervised information from images is made possible.
However in the previous works, little attention has been paid to using such unsupervised information for task of zero-shot learning.
In this work, we first propose a multi-task neural network to predict attributes from images while exploiting this unsupervised information
in order to mitigate the so called \textit{domain shift problem} in predictions on unseen data.
We also propose a novel semi-supervised zero-shot learning method that works on an embedding space corresponding to
abstract deep visual features. We seek a linear transformation on signatures to map them onto the visual features,
such that the mapped signatures of the seen classes are close to labeled samples of the corresponding
classes and unlabeled data are also close to the mapped signatures of one of the unseen classes.
 We use the idea that the rich deep visual features provide a representation
 space in which samples of each class are usually condensed in a cluster. The effectiveness of the proposed method is demonstrated through extensive
experiments on four public benchmarks improving the state-of-the-art prediction accuracy on three of them.

\bigskip\noindent\textbf{Keywords}:
Zero-shot Learning, Semi-supervised Learining, Deep Learning, Representation Learning.
\end{latin}

\newpage
